Precise Weed and Maize classification through Convolutional Neuronal Networks

### 2017-07-21 PaperBCJ.tex
cambios21julio
cambio 7 am

For this stage, another dataset with 202 images of maize plants in stage V3-V7 and 202 images of weeds were considered, obtained in different maize crops that the training dataset. For this test and in order to have a reliable value its considered to classify ten times the dataset, so the average time of classification by image was obtained with the chosen hardware, we started the classification in Caffe without modifications in Software. The results were comparated between cNET with 64 and 16 filters and there are shown in the next Table \ref{table:4}.\\

@@

Like the table shown the best results in times of classification were achieved by the GPU processor, it is the best option to classificate a large amount of images however this project is thought to be portable, so the Raspberry Pi were considered for the analysis of classification performance. With cNET of 64 filters the results of time of classification was 615 miliseconds, so it time isn\'t the optimum for our objective that it is the approximation to classification in a real time.\\

@@

The results shown previously are not definitive because Caffe has ways to optimize the classification of datasets of images, for this document batching was used to classify the dataset of each class in a single forward pass and the use of Multithreading by OpenBLAS math software. For each hardware, Caffe were recompiled with OpenBLAS instead of Atlas, in the program all images  were entered in a vector to be classified in an only batch per each class, also OpenBLAS was configured to use the 4 cores of each hardware to obtain fair results, the obtained results are the following \\

@@

The results show that for the GPU Classification time it has worsened by 66 \%, mainly because the OpenBLAS Library makes extensive use of the CPU threads causing that not all parameters will be computed by GPU as in the previous test. Instead, when the CPU is used the results are better, because the operations are executed using each of the four cores, in the case of the CPU we notice a 22 \% and for 6.3 \% for the Raspberry Pi \\

>>>>

For this stage, another dataset was considered with 202 images of maize plants in stage V3-V7 and 202 images of weeds, obtained in different maize crops than the ones used for the the training dataset. In order to have a reliable value for this test its considered to classify ten times the dataset (CLARIFICAR IDEA). The average image classification time was obtained with the chosen hardware, the classification started in Caffe without modifications in the software. The results were comparated between cNET arquitecture with 64 and 16 filters, these are shown in the next Table \ref{table:4}.\\

@@

As the table shows, the best results in classification time were achieved by the GPU processor, thus it is the best option to classify a large amount of images. However this project is thought to be portable, so the Raspberry Pi was selected for the classification performance analysis. Despite the fact that the classification time resul for the cNET of 64 filters was 615 miliseconds, this  time is not optimum for the approximation of real time classification.\\

@@

The results shown previously are not definitive because Caffe has ways to optimize image dataset classification. In this research project, batching was used to classify the dataset of each class in a single forward pass and the use of Multithreading by OpenBLAS math software (ORDENAR IDEA). For each hardware, Caffe was recompiled with OpenBLAS instead of Atlas. In the program, all images  were entered in a vector to be classified in an only batch per each class. Also, OpenBLAS was configured to use the 4 cores of each hardware to obtain fair results, the obtained results are the following. \\

@@

The results show that for the GPU classification time has decreased by 66 \%, mainly because the OpenBLAS Library makes an extensive use of the CPU threads, causing that not all parameters will be computed by GPU as in the previous test. Instead, when the CPU is used the results are better, because the operations are executed using each of the four cores. In the case of the CPU, otice a 22 \% and for 6.3 \% for the Raspberry Pi \\
